Cycle Route Uptake and Scenario Estimation (CRUSE): an approach for developing strategic cycle network planning tools

### 2024-03-24 paper.qmd
Final tweaks to abstract

# # Uncomment the following line to produce the cover page
author:
  - name: Robin Lovelace
    email: r.lovelace@leeds.ac.uk
    corresponding: true
    affiliations:
      - name: University of Leeds
        address: Institute for Transport Studies, Leeds, LS2 9JT, United Kingdom
  - name: Joey Talbot
    affiliations:
      - name: University of Leeds
        address: Institute for Transport Studies, Leeds, LS2 9JT, United Kingdom
  - name: Eugeni Vidal-Tortosa
    affiliations:
      - name: University of Leeds
        address: Institute for Transport Studies, Leeds, LS2 9JT, United Kingdom
  - name: Hussein Mahfouz
    affiliations:
      - name: University of Leeds
        address: Institute for Transport Studies, Leeds, LS2 9JT, United Kingdom
  - name: Elaine Brick
    affiliations:
      - name: AECOM
        address: Unit 6, Galway Technology Park, Parkmore, Galway, Ireland
  - name: Peter Wright
    affiliations:
      - name: AECOM
        address: Winslade House, Winslade Park, Manor Drive, Clyst St Mary, Exeter, EX5 1FY, UK
  - name: "Gary O'Toole"
    affiliations:
      - name: AECOM
        address: Unit 6, Galway Technology Park, Parkmore, Galway, Ireland
  - name: Dan Brennan
    affiliations:
      - name: Transport Infrastructure Ireland
        address: Parkgate Business Centre, Parkgate Street, Dublin 8, D08 DK10, Ireland
  - name: Suzanne Meade
    affiliations:
      - name: Transport Infrastructure Ireland
        address: Parkgate Business Centre, Parkgate Street, Dublin 8, D08 DK10, Ireland
abstract: |
  This paper describes an approach for developing strategic cycle network planning tools. Based on our experience developing and deploying the Cycle Route Uptake and Scenario Estimation (CRUSE) Tool for Ireland, we outline the underlying methods, including disaggregation of origin-destination data, incorporation of additional trip purposes, routing, scenarios generation, and development of an intuitive user interface. Commissioned and used by Transport Infrastructure Ireland, CRUSE provides estimates of current and potential future cycling levels under 'snapshot' scenarios to inform investment decisions. The publicly available results at https://cruse.bike/ enable planners, engineers, and other stakeholders to make more evidence-based decisions. CRUSE goes beyond previous work by: modeling networks at high spatial resolution; simulating multiple trip purposes (social, shopping, personal utility, recreational, and cycle touring) in addition to using official origin-destination data; and providing estimates of 'quietness' (a proxy for cyclist comfort) at the route segment level. Three network types --- 'Fastest', 'Balanced', and 'Quietest' --- help plan both arterial and residential cycle networks. Workshops and unstructured interviews with stakeholders show that the tool is already being used in practice to inform urban, inter-urban, and rural network plans. The approach is flexible and open-source, allowing the underlying ideas and code to be adapted, supporting effective cycling policies and interventions internationally.
keywords: 
  - Cycling
  - Open-source
  - Road Safety
  - Active Travel
date: last-modified
---

>>>>

# # Uncomment the following line to produce the cover page
author:
  - name: Robin Lovelace
    email: r.lovelace@leeds.ac.uk
    corresponding: true
    affiliations:
      - name: University of Leeds
        address: Institute for Transport Studies, Leeds, LS2 9JT, United Kingdom
  - name: Joey Talbot
    affiliations:
      - name: University of Leeds
        address: Institute for Transport Studies, Leeds, LS2 9JT, United Kingdom
  - name: Eugeni Vidal-Tortosa
    affiliations:
      - name: University of Leeds
        address: Institute for Transport Studies, Leeds, LS2 9JT, United Kingdom
  - name: Hussein Mahfouz
    affiliations:
      - name: University of Leeds
        address: Institute for Transport Studies, Leeds, LS2 9JT, United Kingdom
  - name: Elaine Brick
    affiliations:
      - name: AECOM
        address: Unit 6, Galway Technology Park, Parkmore, Galway, Ireland
  - name: Peter Wright
    affiliations:
      - name: AECOM
        address: Winslade House, Winslade Park, Manor Drive, Clyst St Mary, Exeter, EX5 1FY, UK
  - name: "Gary O'Toole"
    affiliations:
      - name: AECOM
        address: Unit 6, Galway Technology Park, Parkmore, Galway, Ireland
  - name: Dan Brennan
    affiliations:
      - name: Transport Infrastructure Ireland
        address: Parkgate Business Centre, Parkgate Street, Dublin 8, D08 DK10, Ireland
  - name: Suzanne Meade
    affiliations:
      - name: Transport Infrastructure Ireland
        address: Parkgate Business Centre, Parkgate Street, Dublin 8, D08 DK10, Ireland
abstract: |
  This paper describes an approach for developing strategic cycle network planning tools. Based on our experience developing and deploying the Cycle Route Uptake and Scenario Estimation (CRUSE) Tool for Ireland, we outline the underlying methods, including disaggregation of origin-destination data, incorporation of additional trip purposes, routing, scenario generation, and development of an intuitive user interface. Commissioned and used by Transport Infrastructure Ireland, CRUSE provides estimates of current and potential future cycling levels under 'snapshot' scenarios to inform investment decisions. The publicly available results at https://cruse.bike/ enable planners, engineers, and other stakeholders to make more evidence-based decisions. CRUSE goes beyond previous work by: modeling networks at high spatial resolution; simulating multiple trip purposes (social, shopping, personal utility, recreational, and cycle touring) in addition to using official origin-destination data; and providing estimates of 'quietness' (a proxy for cyclist comfort and route preference) at the route segment level. Three network types --- 'Fastest', 'Balanced', and 'Quietest' --- help plan both arterial and residential cycle networks. Workshops and unstructured interviews with stakeholders show that the tool is already being used in practice to inform urban, inter-urban, and rural network planning. The approach is flexible and open-source, allowing the underlying ideas and code to be adapted, supporting effective cycling policies and interventions internationally.
keywords: 
  - Cycling
  - Open-source
  - Road Safety
  - Active Travel
date: last-modified
---

### 2024-03-24 paper.tex
Final tweaks to abstract

\begin{abstract}
This paper describes an approach for developing strategic cycle network
planning tools. Based on our experience developing and deploying the
Cycle Route Uptake and Scenario Estimation (CRUSE) Tool for Ireland, we
outline the methods used to generate the evidence presented in the tool,
including disaggregation of origin-destination data, additional trip
purposes, routing, scenarios of cycling potential, and the user
interface. Commissioned and used by Transport Infrastructure Ireland,
CRUSE provides estimates of cycling currently and under `snapshot'
scenarios of `cycling futures' to inform investment decisions. The
results are publicly available at \url{https://cruse.bike/}, enabling
planners, engineers, and other stakeholders to make more evidence-based
decisions. CRUSE goes beyond previous work by: modelling networks at
high levels of geographic resolution; simulating multiple trip purposes
(social, shopping and personal utility trips plus recreational and cycle
touring trips), in addition to using official data on trips to work and
education locations; and by providing estimates of `quietness' (a proxy
for cyclability) at the route segment level. Three network types ---
`Fastest', `Balanced' and `Quietest' --- help plan both arterial and
residential cycle networks. Workshops and unstructured interviews of
stakeholders show that the tool is already being used in practice, to
inform urban, inter-urban and rural network development. The approach is
flexible and open, allowing the underlying ideas and code to be used in
other places to generate the evidence needed for effective cycling
policies and interventions internationally.
\end{abstract}

>>>>

\begin{abstract}
This paper describes an approach for developing strategic cycle network
planning tools. Based on our experience developing and deploying the
Cycle Route Uptake and Scenario Estimation (CRUSE) Tool for Ireland, we
outline the underlying methods, including disaggregation of
origin-destination data, incorporation of additional trip purposes,
routing, scenarios generation, and development of an intuitive user
interface. Commissioned and used by Transport Infrastructure Ireland,
CRUSE provides estimates of current and potential future cycling levels
under `snapshot' scenarios to inform investment decisions. The publicly
available results at https://cruse.bike/ enable planners, engineers, and
other stakeholders to make more evidence-based decisions. CRUSE goes
beyond previous work by: modeling networks at high spatial resolution;
simulating multiple trip purposes (social, shopping, personal utility,
recreational, and cycle touring) in addition to using official
origin-destination data; and providing estimates of `quietness' (a proxy
for cyclist comfort) at the route segment level. Three network types ---
`Fastest', `Balanced', and `Quietest' --- help plan both arterial and
residential cycle networks. Workshops and unstructured interviews with
stakeholders show that the tool is already being used in practice to
inform urban, inter-urban, and rural network plans. The approach is
flexible and open-source, allowing the underlying ideas and code to be
adapted, supporting effective cycling policies and interventions
internationally.
\end{abstract}
